---
date: "`r Sys.Date()`"
output:
  html_document:
    code_folding: "hide"
---


```{r setup, include=FALSE, echo = FALSE}
# Basic knitr options
library(knitr)
opts_chunk$set(comment = NA, 
               echo = TRUE,
               warning = FALSE, 
               message = FALSE, 
               error = TRUE, 
               cache = FALSE,
               fig.width = 9.64,
               fig.height = 5.9,
               fig.path = 'figures/')

## Load libraries
library(ggplot2)
library(lubridate)
library(dplyr)
library(ggplot2)
library(sp)
library(raster)
library(viridis)
library(ggthemes)
library(sf)
library(rnaturalearth)
library(rnaturalearthdata)
library(RColorBrewer)
library(readr)
library(zoo)
library(tidyr)
options(scipen = '999')
library(bohemia)
library(leaflet)
library(geosphere)
library(leafpop)

# Define function for pretty tables
prettify <- function(the_table,
                     remove_underscores_columns = TRUE,
                     cap_columns = TRUE,
                     cap_characters = TRUE,
                     comma_numbers = TRUE,
                     date_format = '%B %d, %Y',
                     round_digits = 2,
                     remove_row_names = TRUE,
                     remove_line_breaks = TRUE,
                     data_table = TRUE,
                     nrows = 5,
                     download_options = FALSE,
                     scroll_x = TRUE){
  
  column_names <- names(the_table)
  the_table <- data.frame(the_table)
  names(the_table) <- column_names
  classes <- lapply(the_table, function(x){unlist(class(x))[1]})
  
  if(cap_columns){
    names(the_table) <- Hmisc::capitalize(names(the_table))
  }
  
  if(remove_underscores_columns){
    names(the_table) <- gsub('_', ' ', names(the_table))
  }
  
  for (j in 1:ncol(the_table)){
    the_column <- the_table[,j]
    the_class <- classes[j][1]
    if(the_class %in% c('character', 'factor')){
      if(cap_characters){
        the_column <- as.character(the_column)
        the_column <- Hmisc::capitalize(the_column)
      }
      if(remove_line_breaks){
        the_column <- gsub('\n', ' ', the_column)
      }
    } else if(the_class %in% c('POSIXct', 'Date')){
      the_column <- format(the_column, format = date_format)
    } else if(the_class %in% c('numeric', 'integer')){
      the_column <- round(the_column, digits = round_digits)
      # if(comma_numbers){
      #   left <- scales::comma(the_column)
      # }
    }
    the_table[,j] <- the_column
  }
  if(remove_row_names){
    row.names(the_table) <- NULL
  }
  if(data_table){
    if(download_options){
      the_table <- DT::datatable(the_table,
                                 options = list(pageLength = nrows,
                                                # buttons = c('copy',
                                                #             'csv',
                                                #             'excel',
                                                #             'pdf'),
                                                dom = 'Bfrtip',
                                                scrollX = scroll_x,
                                                buttons = 
                                                  list('copy', 'print', list(
                                                    extend = 'collection',
                                                    buttons = 'csv',# c('csv', 'excel', 'pdf'),
                                                    text = 'Download'
                                                  ))),
                                 rownames = FALSE,
                                 extensions = 'Buttons')
    } else {
      the_table <- DT::datatable(the_table,
                                 options = list(pageLength = nrows,
                                                scrollX = scroll_x,
                                                columnDefs = list(list(className = 'dt-right', 
                                                                       targets = 0:(ncol(the_table) - 1)))),
                                 rownames = FALSE)
    }
    
  }
  return(the_table)
}

# Define function for calculating distance
calculate_distance <- function(shp, lat, lng){
  p <- c(lng, lat)
  # ll <- length(shp@polygons[[1]]@Polygons)
  ll <- nrow(coordinates(shp))
  out_list <- list()
  for(i in 1:ll){
    temp_points <- coordinates(shp)[i,]#shp@polygons[[1]]@Polygons[[ll]]@coords
    out_list[[i]] <- temp_points
  }
  the_points <- do.call('rbind', out_list)
  the_line <- SpatialPointsDataFrame(coords = the_points,
                                     data = data.frame(id = 1:nrow(the_points)))
  proj4string(the_line) <- proj4string(shp)
  i = 1
  out <- rep(NA, nrow(the_points))
  for(i in 1:nrow(the_points)){
    out[i] <- distm(c(the_points[i,]), c(lng, lat), fun = distHaversine)
  }
  df <- data.frame(the_points)
  df$distance <- out
  df$lng <- lng
  df$lat <- lat
  return(df)
}

# Load artefacts from recon_clustering.R

load('final/clusters.RData')
load('final/buffers.RData')
load('final/cores.RData')
load('households_spatial.RData')
load('registrations.RData')
load('shapefiles.RData')
load('inclusion.RData')
```

```{r}
# Determine which households are in which clusters, cores, buffers
o <- sp::over(households_spatial, polygons(clusters))
households_spatial@data$cluster_number <- clusters@data$cluster_number[o]
o <- sp::over(households_spatial, polygons(cores))
households_spatial@data$core_number <- cores@data$cluster_number[o]
o <- sp::over(households_spatial, polygons(buffers))
households_spatial@data$buffer_number <- buffers@data$cluster_number[o]
households_spatial@data$in_core <- 
  !is.na(households_spatial@data$core_number)

# Associate relevant registrations data with households
cha_matcher <- registrations %>%
  filter(worker_type == 'CHV') %>%
  dplyr::select(wid_cha, wid) %>%
  filter(!is.na(wid_cha)) %>%
  dplyr::distinct(wid, .keep_all = TRUE)

# Get aggregate counts per cluster
agg <- households_spatial@data %>%
  # Get cha wid
  left_join(cha_matcher) %>%
  # filter out those which are not in study
  filter(!is.na(cluster_number)) %>%
  group_by(cluster_number) %>%
  summarise(households_core_and_buffer = n(),
            households_core = length(which(!is.na(core_number))),
            households_buffer = length(which(!is.na(buffer_number))),
            members_core_and_buffer = sum(num_hh_members),
            members_core = sum(num_hh_members[!is.na(core_number)]),
            members_buffer = sum(num_hh_members[!is.na(buffer_number)]),
            members_gt_5_core_and_buffer = sum(num_hh_members_bt_5_15 + num_hh_members_gt_15),
            members_bt_5_15_core = sum(num_hh_members_bt_5_15[!is.na(core_number)]),
            community_health_units = paste0(sort(unique(community_health_unit)), collapse = ';'),
            wards = paste0(sort(unique(ward)), collapse = ';'),
            villages = paste0(sort(unique(village)), collapse = ';'),
            chvs = paste0(sort(unique(wid)), collapse = ';'),
            chas = paste0(sort(unique(wid_cha)), collapse = ';'))
```

```{r}
# Create outputs for Virginia Teach with cluster information
if(FALSE){
  vt <- households_spatial@data %>% filter(!is.na(cluster_number)) %>%
    dplyr::select(-core_number, -buffer_number)
  write_csv(vt, '~/Desktop/recon_only_in_study_with_cluster_info.csv')
}
```

## Bohemia Kenya clusters {.tabset .tabset-fade}


### Table

```{r}
prettify(agg, nrows = nrow(agg), download_options = TRUE)
```

### Static maps

#### Clusters

```{r}
clusters_fortified <- fortify(clusters, id = clusters@data$cluster_number)
cores_fortified <- fortify(cores, id = cores@data$cluster_number)
buffers_fortified <- fortify(buffers, id = buffers@data$cluster_number)
centroids <- coordinates(clusters)
centroids_df <- data.frame(centroids)
centroids_df <- centroids_df %>%
  dplyr::rename(longitude = X1,
                latitude = X2) %>%
  mutate(cluster_number = clusters@data$cluster_number)

g <- ggplot() +
  geom_polygon(data = pongwe_kikoneni_ramisi_fortified,
               aes(x = long,
                   y = lat,
                   group = group),
               color = 'black',
               fill = 'beige') +
  labs(x = 'Longitude',
       y = 'Latitude') +
  theme_bw() +
  coord_map() 
g +
  geom_polygon(data = clusters_fortified,
               aes(x = long,
                   y = lat,
                   group = group),
               fill = 'black',
               alpha = 0.7,
               color = 'black') +
  geom_text(data = centroids_df,
            aes(x = longitude,
                y = latitude, 
                label = cluster_number),
            size = 2,
            alpha = 0.8,
            color = 'white')
    
```

#### Buffers

```{r}
g +
  geom_polygon(data = buffers_fortified %>% filter(!is.na(hole)),
               aes(x = long,
                   y = lat,
                   group = group),
               fill = NA,
               alpha = 0.5,
               color = 'red') 
```

#### Cores

```{r}
g +
  geom_polygon(data = cores_fortified %>% filter(!is.na(hole)),
               aes(x = long,
                   y = lat,
                   group = group),
               fill = 'red',
               alpha = 0.5,
               color = 'red') 
```


### Interactive map

```{r, eval = TRUE}
map_clusters <- clusters
map_clusters@data <- left_join(map_clusters@data, agg)

map_clusters@data <- map_clusters@data %>%
  mutate(popup = paste0('Cluster ', cluster_number),
         label = paste0('. Households: ', households_core_and_buffer, ' (',
                        households_core, ' in core, ', households_buffer, ' in buffer). ',
                        'Members: ', members_core_and_buffer, ' (',
                        members_core, ' in core, ', members_buffer, ' in buffer)'))

map_cores <- cores
map_cores@data <- left_join(map_cores@data, agg)
map_cores@data <- map_cores@data %>%
  mutate(label = paste0('Core of cluster ', cluster_number)) %>%
  mutate(popup = paste0('Cluster ', cluster_number))



# Plot into leaflet map
library(leaflet)
library(leaflet.extras)
library(raster)
# pal <- colorNumeric(c("blue", "white", "red"), values(study_area),
#                     na.color = "transparent")
# xpal <- colorNumeric("Spectral", hfj@data$cases, reverse = TRUE)

map <- leaflet() %>%
  addProviderTiles(providers$Stamen.Toner, group = "Basic") %>%
  addProviderTiles(providers$OpenStreetMap, group = "OSM") %>%
  addProviderTiles(providers$Esri.WorldImagery, group = "Satellite")

# Add social science households
ss <- inclusion

# map <- map %>%
  # addRasterImage(study_area, colors = pal, opacity = 0.8,
  #                group = 'PAPfPR') %>%
  # addLegend(pal = pal, values = values(study_area),
  #           title = "PAPfPR", group = 'PAPfPR')
# map <- map %>%
#   addCircleMarkers(data = hfj, color = xpal(hfj@data$cases),
#                    label = paste0(hfj@data$Facility_Name,
#                                   ": ", hfj@data$cases),
#                    fillOpacity = 1,
#                    group = 'Health facilities',
#                    radius = 10) %>%
#   addLegend("bottomleft", pal = xpal, values = hfj@data$cases,
#             title = "2021 malaria cases", opacity = 1,
#             group = 'Health facilities')

map <- map %>%
  addCircleMarkers(data = households_spatial,
                   opacity = 1,
                   color = 'black',
                   radius = 0.5,
                   fillOpacity = 1, 
                   weight = 1,
                   group = 'Households',
                   popup = households_spatial@data$hh_id,
                   label = paste0(households_spatial@data$hh_id, '. ', households_spatial@data$num_hh_members, ' members'))
map <- map %>%
  addCircleMarkers(data = ss, color = 'orange',
                   label = paste0('Social science household ',
                                  ": ", ss@data$hh_id),
                   group = 'Social science households',
                   radius = 1,
                   fillOpacity = 1, 
                   weight = 1) 
mydrawPolylineOptions <- function (allowIntersection = TRUE, 
                                   drawError = list(color = "#b00b00", timeout = 2500), 
                                   guidelineDistance = 20, metric = TRUE, feet = FALSE, zIndexOffset = 2000, 
                                   shapeOptions = drawShapeOptions(fill = FALSE), repeatMode = FALSE) {
  leaflet::filterNULL(list(allowIntersection = allowIntersection, 
                           drawError = drawError, guidelineDistance = guidelineDistance, 
                           metric = metric, feet = feet, zIndexOffset = zIndexOffset,
                           shapeOptions = shapeOptions,  repeatMode = repeatMode)) }

map <- map %>%
  addLayersControl(
    baseGroups = c("Basic", "OSM", "Satellite"),
    overlayGroups = c(#"Hamlet centroids", 
      #'PAPfPR',
      #'Health facilities',
      'Households',
      'Social science households'),
    options = layersControlOptions(collapsed = FALSE)
  ) %>% addFullscreenControl() %>% 
  addDrawToolbar(
    polylineOptions = mydrawPolylineOptions(metric=TRUE, feet=FALSE),
    editOptions=editToolbarOptions(selectedPathOptions=selectedPathOptions())
  ) 

map <- map %>%
  addPolygons(data = map_clusters, weight = 1, fillOpacity = 0.3, popup = map_clusters@data$popup, label = map_clusters@data$label) %>%
  addPolygons(data = map_cores, fillColor = 'red', weight = 1, fillOpacity = 0.3, popup = map_cores@data$popup, label = map_cores@data$label)

map

# htmltools::save_html(map, file = 'map.html')
htmlwidgets::saveWidget(widget = map,
                        file = 'kenyaclusters.html',
                        selfcontained = TRUE)

```

### Stats

#### Overall numbers

```{r}
# Total details
agg2 <- households_spatial@data %>%
  # filter out those which are not in study
  filter(!is.na(cluster_number)) %>%
  summarise(households_core_and_buffer = n(),
            households_core = length(which(!is.na(core_number))),
            households_buffer = length(which(!is.na(buffer_number))),
            members_core_and_buffer = sum(num_hh_members),
            members_core = sum(num_hh_members[!is.na(core_number)]),
            members_buffer = sum(num_hh_members[!is.na(buffer_number)]),
            members_gt_5_core_and_buffer = sum(num_hh_members_bt_5_15 + num_hh_members_gt_15),
            members_bt_5_15_core = sum(num_hh_members_bt_5_15[!is.na(core_number)]),
            community_health_units = paste0(sort(unique(community_health_unit)), collapse = ';'))
prettify(agg2)
```

#### Distribution of cluster size (households, core and buffer)

```{r}
ggplot(data = agg,
       aes(x = households_core_and_buffer)) +
  geom_histogram(fill = 'lightblue',
                 color = 'black') +
  theme_bw() +
  labs(x = '',
       y = 'Count')
```

#### Distribution of cluster size (members, core and buffer)

```{r}
ggplot(data = agg,
       aes(x = members_core_and_buffer)) +
  geom_histogram(fill = 'lightblue',
                 color = 'black') +
  theme_bw() +
  labs(x = '',
       y = 'Count')
```

#### Distribution of cluster size (members 5-15, core and buffer)

```{r}
ggplot(data = agg,
       aes(x = members_bt_5_15_core)) +
  geom_histogram(fill = 'lightblue',
                 color = 'black') +
  theme_bw() +
  labs(x = '',
       y = 'Count')
```

#### How to divide 275 fieldworkers

Assuming fieldworker distribution should be only a function of the number of 5+ year-olds in clusters (cores and buffers combined), and assuming that there are a total of 275 fieldworkers, then the correct number of people per fieldworker would be:

```{r}
five_pluses_per_fw <- agg2$members_gt_5_core_and_buffer / 275
five_pluses_per_fw
```

The below table shows how many fieldworkers should be assigned per cluster. It is intentionally not-rounded so as to facilitate decision-making.

```{r}
agg %>%
  dplyr::select(cluster_number, members_gt_5_core_and_buffer) %>%
  mutate(fieldworkers = members_gt_5_core_and_buffer / five_pluses_per_fw) %>% 
  prettify(download_options = TRUE, nrows = nrow(.))
```
