---
output: pdf_document
header-includes:
- \usepackage{booktabs}
- \usepackage{longtable}
- \usepackage{array}
- \usepackage{multirow}
- \usepackage{wrapfig}
- \usepackage{float}
- \usepackage{colortbl}
- \usepackage{pdflscape}
- \usepackage{tabu}
- \usepackage{threeparttable}
- \usepackage[normalem]{ulem}
geometry: margin=1cm
classoption: landscape
---


```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = NA, 
               echo = FALSE, 
               warning = FALSE, 
               message = FALSE, 
               error = TRUE, 
               cache = FALSE,
  fig.path = "figures/",
  out.width = "100%"
)
options(knitr.kable.NA = '')
```

```{r}
library(dplyr)
library(knitr)
options(digits=8)

library(kableExtra)
library(readr)
library(dplyr)
library(tools)
```

```{r}
# Read in the randomization results
hh <- read_csv('../hh.csv')
# Get the list of clusters
clusters <- sort(unique(hh$cluster))
pgs <- sort(unique(hh$pg))

```


\pagenumbering{gobble} 

```{r results='asis'}  
# Print the titles/tables
# for (i in 1:length(clusters)) {
for(i in 1:length(pgs)){
  # this_cluster <- clusters[i]
  this_pg <- pgs[i]
  this_data <- hh %>%
    filter(pg == this_pg) #%>%
    # filter(cluster == this_cluster) %>%
    # arrange(map_recon_HHID)
  this_cluster <- this_data$cluster[1]
  this_letter <- this_data$let[1]
  # Get the number of casual laborers associated with the cluster
  # n_cls <- fw_per_cluster %>% filter(cluster == this_cluster) %>% dplyr::pull(cls)
  
  this_data$cluster <- NULL
  this_data$roof_material <- gsub('_', ' ', this_data$roof_material)
  this_data$roof_material <- tools::toTitleCase(this_data$roof_material)

  this_data$wall_material <- gsub('_', ' ', this_data$wall_material)
  this_data$wall_material <- tools::toTitleCase(this_data$wall_material)
  
  this_data$pg <- this_data$let <- NULL

  names(this_data) <- gsub('_', ' ', names(this_data))
  
  this_data$`New household ID` <- '       '
  this_data$Notes <- '       '

  # names(this_data) <- Hmisc::capitalize(names(this_data))
  names(this_data) <- tools::toTitleCase(names(this_data))
  k <- kable(this_data, format = "latex",
              longtable = TRUE,
              booktabs = TRUE,
              #align = "c", 
          row.names = FALSE,
          align=rep('c', ncol(this_data))) %>%
      kable_styling(latex_options = c(#"scale_down",
                                       "striped",
                                       'repeat_header'
                                      ), 
                     # full_width = T, 
                    font_size = 9) %>%
    column_spec(8, width = "18em") %>%
  add_header_above(c(" " = 2,
                     "(Locus GIS)" = 1,
                     "(Door)" = 1,
                     " " = 2,
                     "(Barcode)" = 1,
                     " " = 1),
                   underline = FALSE,
                   line = FALSE)
  cat(paste0('# Cluster ', this_cluster, ' - ', this_letter,  '\n\n'))
  # k <- paste0(paste0('Cluster ', this_cluster, '\\', k))
  print(k)
  cat('\\newpage')
}
