---
title: "Visit control sheets - Visit 0"
output: pdf_document
header-includes:
- \usepackage{booktabs}
- \usepackage{longtable}
- \usepackage{array}
- \usepackage{multirow}
- \usepackage{wrapfig}
- \usepackage{float}
- \usepackage{colortbl}
- \usepackage{pdflscape}
- \usepackage{tabu}
- \usepackage{threeparttable}
- \usepackage[normalem]{ulem}
geometry: margin=1cm
classoption: landscape
---


```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = NA, 
               echo = FALSE, 
               warning = FALSE, 
               message = FALSE, 
               error = TRUE, 
               cache = FALSE,
  fig.path = "figures/",
  out.width = "100%"
)
options(knitr.kable.NA = '')
```

```{r}
library(dplyr)
library(knitr)
options(digits=8)

library(kableExtra)
library(readr)
library(dplyr)
library(tools)
```

```{r}
# Read in the randomization results
hh <- read_csv('../hh.csv')
# Get the list of clusters
clusters <- sort(unique(hh$cluster))

```

\newpage

\pagenumbering{gobble} 

```{r results='asis'}  
# Print the titles/tables
for (i in 1:length(clusters)) {
  this_cluster <- clusters[i]
  this_data <- hh %>% filter(cluster == this_cluster) %>%
    arrange(map_recon_HHID)
  this_data$cluster <- NULL
  this_data$roof_material <- gsub('_', ' ', this_data$roof_material)
  this_data$roof_material <- tools::toTitleCase(this_data$roof_material)

  this_data$wall_material <- gsub('_', ' ', this_data$wall_material)
  this_data$wall_material <- tools::toTitleCase(this_data$wall_material)

  names(this_data) <- gsub('_', ' ', names(this_data))
  this_data$Notes <- '       '

  # names(this_data) <- Hmisc::capitalize(names(this_data))
  names(this_data) <- tools::toTitleCase(names(this_data))
  k <- kable(this_data, format = "latex",
              longtable = TRUE,
              booktabs = TRUE,
              #align = "c", 
          row.names = FALSE) %>%
      kable_styling(latex_options = c(#"scale_down",
                                       "striped"
                                      ), 
                     # full_width = T, 
                    font_size = 9) %>%
    column_spec(8, width = "18em")
  cat(paste0('# Cluster ', this_cluster, '\n\n'))
  # k <- paste0(paste0('Cluster ', this_cluster, '\\', k))
  print(k)
  cat('\\newpage')
}
