---
title: "Clusters and CHV areas of work"
author: "Databrew"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE, echo = FALSE}
# Basic knitr options
library(knitr)
opts_chunk$set(comment = NA, 
               echo = FALSE,
               warning = FALSE, 
               message = FALSE, 
               error = TRUE, 
               cache = FALSE,
               fig.width = 9.64,
               fig.height = 5.9,
               fig.path = 'figures/')
```

```{r}
library(paws)
library(dplyr)
library(readr)
library(ggplot2)
library(rgdal)
library(raster)
library(ggthemes)
library(sp)

# Load in spatial polygons
load('../recon_clustering/final/cores.RData')
load('../recon_clustering/final/buffers.RData')
load('../recon_clustering/final/clusters.RData')
load('../recon_clustering/registrations.RData')

# Load in recon data
# https://s3.console.aws.amazon.com/s3/object/databrew.org?region=us-east-1&prefix=kwale/recon/clean-form/reconbhousehold/reconbhousehold.csv
recon <- read_csv('from_aws/reconbhousehold.csv')
# https://s3.console.aws.amazon.com/s3/object/databrew.org?region=us-east-1&prefix=kwale/recon/clean-form/reconbhousehold/curated_recon_household_data.csv
recon_curated <- read_csv('from_aws/curated_recon_household_data.csv')

# Read in and organize recon data
hhsp <- readOGR('../../data_public/spatial/households/', 'households')
hhsp@data <- left_join(hhsp@data %>% dplyr::rename(hh_id_clean = hh_id) %>% dplyr::select(-village, ward),
                       recon_curated %>% dplyr::select(hh_id_raw, hh_id_clean,
                                                       community_health_unit,
                                                       village,
                                                       ward))
# See if in cluster core / buffer
o <- sp::over(hhsp, polygons(clusters))
hhsp@data$cluster <- clusters@data$cluster_number[o]
o <- sp::over(hhsp, polygons(buffers))
hhsp@data$buffer <- buffers@data$cluster_number[o]
o <- sp::over(hhsp, polygons(cores))
hhsp@data$core <- cores@data$cluster_number[o]
# Keep only those which are in clusters
hhsp <- hhsp[!is.na(hhsp@data$cluster),]
# Define buffer / core status
hhsp@data$core_buffer <- ifelse(!is.na(hhsp@data$core), 'Core',
                                ifelse(!is.na(hhsp@data$buffer), 'Buffer', NA))
hhsp@data$core_buffer <- factor(hhsp@data$core_buffer, levels = c('Core', 'Buffer'))
hhsp <- hhsp[!is.na(hhsp@data$core_buffer),]


# For each community health unit, get the clusters
x <- hhsp@data %>%
  group_by(community_health_unit, cluster) %>%
  summarise(hh = n()) %>%
  ungroup

# Do by chu
by_chu <- x %>%
  arrange(desc(hh)) %>%
  group_by(community_health_unit) %>%
  summarise(n_clusters = n(),
            n_households = sum(hh),
            clusters = paste0('Cluster ', cluster, ' (', hh, ' households)', collapse = '<br>'))
names(by_chu) <- toupper(names(by_chu))
names(by_chu) <- gsub('_', ' ', names(by_chu))
dt <- DT::datatable(by_chu, escape = FALSE,
              options = list(
                paging =TRUE,
                pageLength =  nrow(by_chu)
              ))
# htmltools::save_html(dt, file = '~/Desktop/by_chu.html')
# htmlwidgets::saveWidget(dt, file = 'chu.html')
```

# Which clusters are in each CHU (community health unit)?

```{r}
dt
```

# Which CHUs are in each cluster?

```{r}
# Do by chu
by_cluster <- x %>%
  arrange(desc(hh)) %>%
  group_by(cluster) %>%
  summarise(n_chus = n(),
            n_households = sum(hh),
            chus = paste0('CHU ', community_health_unit, ' (', hh, ' households)', collapse = '<br>'))
names(by_cluster) <- toupper(names(by_cluster))
names(by_cluster) <- gsub('_', ' ', names(by_cluster))
dt <- DT::datatable(by_cluster, escape = FALSE,
              options = list(
                paging =TRUE,
                pageLength =  nrow(by_cluster)
              ))
dt
```

# Which clusters are in each CHU (community health unit)?

```{r}
dt
```

# In which cluster does each CHV work (per recon geocoding)?

```{r}
pd <- recon %>%
  mutate(wid = ifelse(is.na(wid_qr), wid_manual, wid_qr)) %>%
  dplyr::select(longitude = Longitude, 
                latitude = Latitude, wid) %>%
  mutate(x = longitude, y = latitude) %>%
  filter(!is.na(longitude))
coordinates(pd) <- ~x+y
proj4string(pd) <-  "+proj=longlat +ellps=WGS84 +datum=WGS84 +no_defs"
o <- sp::over(pd, polygons(clusters))
pd$cluster_number <- clusters$cluster_number[o]
pdx <- pd@data %>%
  filter(!is.na(cluster_number))  %>%
  group_by(wid) %>%
  summarise(n_clusters = length(unique(cluster_number)),
            clusters = paste0(sort(unique(cluster_number)), collapse = '; ')) 
names(pdx) <- toupper(names(pdx))
names(pdx) <- gsub('_', ' ', names(pdx))
dt <- DT::datatable(pdx, escape = FALSE,
              options = list(
                paging =TRUE,
                pageLength =  nrow(pdx)
              ))
dt
```


# Which WID (worker IDs) are associated with each cluster?

```{r}
pd <- recon %>%
  mutate(wid = ifelse(is.na(wid_qr), wid_manual, wid_qr)) %>%
  dplyr::select(longitude = Longitude, 
                latitude = Latitude, wid) %>%
  mutate(x = longitude, y = latitude) %>%
  filter(!is.na(longitude))
coordinates(pd) <- ~x+y
proj4string(pd) <-  "+proj=longlat +ellps=WGS84 +datum=WGS84 +no_defs"
o <- sp::over(pd, polygons(clusters))
pd$cluster_number <- clusters$cluster_number[o]
pdx <- pd@data %>%
  filter(!is.na(cluster_number))  %>%
  group_by(cluster_number) %>%
  summarise(n_wids = length(unique(wid)),
            wids = paste0(sort(unique(wid)), collapse = '; ')) 
names(pdx) <- toupper(names(pdx))
names(pdx) <- gsub('_', ' ', names(pdx))
dt <- DT::datatable(pdx, escape = FALSE,
              options = list(
                paging =TRUE,
                pageLength =  nrow(pdx)
              ))
dt
```

# Which "areas of work" are associated with each cluster?  (using `registration` data)

```{r}
right <- registrations %>%
  filter(worker_type == 'CHV') %>%
  mutate(wid = ifelse(is.na(wid_qr), wid_manual, wid_qr)) %>%
  mutate(areas_of_work = paste0(villages_chv, villages_chv_specify)) %>%
  dplyr::select(areas_of_work, wid)
pd <- recon %>%
  mutate(wid = ifelse(is.na(wid_qr), wid_manual, wid_qr)) %>%
  dplyr::select(longitude = Longitude, 
                latitude = Latitude, wid) %>%
  mutate(x = longitude, y = latitude) %>%
  filter(!is.na(longitude)) %>%
  left_join(right)
coordinates(pd) <- ~x+y
proj4string(pd) <-  "+proj=longlat +ellps=WGS84 +datum=WGS84 +no_defs"
o <- sp::over(pd, polygons(clusters))
pd$cluster_number <- clusters$cluster_number[o]
pdx <- pd@data %>%
  filter(!is.na(cluster_number))  %>%
  group_by(cluster_number) %>%
  summarise(n_villages = length(unique(areas_of_work)),
            villages = paste0(sort(unique(areas_of_work)), collapse = '; ')) 
names(pdx) <- toupper(names(pdx))
names(pdx) <- gsub('_', ' ', names(pdx))
dt <- DT::datatable(pdx, escape = FALSE,
              options = list(
                paging =TRUE,
                pageLength =  nrow(pdx)
              ))
dt
```


# Which clusters are associated with each "area of work"? (using `registration` data)

Note that the "areas of work" question had possibly >1 response, and it's not clear from recon registrations which houses are associated with each

```{r}
right <- registrations %>%
  filter(worker_type == 'CHV') %>%
  mutate(wid = ifelse(is.na(wid_qr), wid_manual, wid_qr)) %>%
  mutate(areas_of_work = paste0(villages_chv, villages_chv_specify)) %>%
  dplyr::select(areas_of_work, wid)
pd <- recon %>%
  mutate(wid = ifelse(is.na(wid_qr), wid_manual, wid_qr)) %>%
  dplyr::select(longitude = Longitude, 
                latitude = Latitude, wid) %>%
  mutate(x = longitude, y = latitude) %>%
  filter(!is.na(longitude)) %>%
  left_join(right)
coordinates(pd) <- ~x+y
proj4string(pd) <-  "+proj=longlat +ellps=WGS84 +datum=WGS84 +no_defs"
o <- sp::over(pd, polygons(clusters))
pd$cluster_number <- clusters$cluster_number[o]
pdx <- pd@data %>%
  filter(!is.na(cluster_number))  %>%
  group_by(areas_of_work) %>%
  summarise(n_clusters = length(unique(cluster_number)),
            clusters = paste0(sort(unique(cluster_number)), collapse = '; ')) 
names(pdx) <- toupper(names(pdx))
names(pdx) <- gsub('_', ' ', names(pdx))
dt <- DT::datatable(pdx, escape = FALSE,
              options = list(
                paging =TRUE,
                pageLength =  nrow(pdx)
              ))
dt
```


# Which "areas of work" are associated with each cluster?  (using `recon` data)

```{r}
pd <- recon %>%
  mutate(wid = ifelse(is.na(wid_qr), wid_manual, wid_qr)) %>%
  dplyr::select(longitude = Longitude, 
                latitude = Latitude, wid,
                areas_of_work = village) %>%
  mutate(x = longitude, y = latitude) %>%
  filter(!is.na(longitude)) 
coordinates(pd) <- ~x+y
proj4string(pd) <-  "+proj=longlat +ellps=WGS84 +datum=WGS84 +no_defs"
o <- sp::over(pd, polygons(clusters))
pd$cluster_number <- clusters$cluster_number[o]
pdx <- pd@data %>%
  filter(!is.na(cluster_number))  %>%
  group_by(cluster_number) %>%
  summarise(n_villages = length(unique(areas_of_work)),
            villages = paste0(sort(unique(areas_of_work)), collapse = '; ')) 
names(pdx) <- toupper(names(pdx))
names(pdx) <- gsub('_', ' ', names(pdx))
dt <- DT::datatable(pdx, escape = FALSE,
              options = list(
                paging =TRUE,
                pageLength =  nrow(pdx)
              ))
dt
```

# Which clusters are associated with each "area of work"? (using `recon`` data)


```{r}
pd <- recon %>%
  mutate(wid = ifelse(is.na(wid_qr), wid_manual, wid_qr)) %>%
  dplyr::select(longitude = Longitude, 
                latitude = Latitude, wid,
                areas_of_work = village) %>%
  mutate(x = longitude, y = latitude) %>%
  filter(!is.na(longitude))
coordinates(pd) <- ~x+y
proj4string(pd) <-  "+proj=longlat +ellps=WGS84 +datum=WGS84 +no_defs"
o <- sp::over(pd, polygons(clusters))
pd$cluster_number <- clusters$cluster_number[o]
pdx <- pd@data %>%
  filter(!is.na(cluster_number))  %>%
  group_by(village = areas_of_work) %>%
  summarise(n_clusters = length(unique(cluster_number)),
            clusters = paste0(sort(unique(cluster_number)), collapse = '; ')) 
names(pdx) <- toupper(names(pdx))
names(pdx) <- gsub('_', ' ', names(pdx))
dt <- DT::datatable(pdx, escape = FALSE,
              options = list(
                paging =TRUE,
                pageLength =  nrow(pdx)
              ))
dt
```


# Map

```{r}
pd <- recon %>%
  mutate(wid = ifelse(is.na(wid_qr), wid_manual, wid_qr)) %>%
  dplyr::select(longitude = Longitude, 
                latitude = Latitude, wid,
                village) %>%
  mutate(x = longitude, y = latitude) %>%
  filter(!is.na(longitude)) 
coordinates(pd) <- ~x+y
proj4string(pd) <-  "+proj=longlat +ellps=WGS84 +datum=WGS84 +no_defs"
library(leaflet)
leaflet() %>%
  addTiles() %>%
  addPolygons(data = clusters, label = clusters$cluster_number,
              popup = clusters$cluster_number) %>%
  addMarkers(data = pd, popup = pd$village, label = pd$village, clusterOptions = markerClusterOptions())
```

