---
title: "Clusters and CHV areas of work"
author: "Databrew"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE, echo = FALSE}
# Basic knitr options
library(knitr)
opts_chunk$set(comment = NA, 
               echo = FALSE,
               warning = FALSE, 
               message = FALSE, 
               error = TRUE, 
               cache = FALSE,
               fig.width = 9.64,
               fig.height = 5.9,
               fig.path = 'figures/')
```

```{r}
library(paws)
library(dplyr)
library(readr)
library(ggplot2)
library(rgdal)
library(raster)
library(ggthemes)
library(sp)
library(bohemia)

# Load in spatial polygons
load('../recon_clustering/final/cores.RData')
load('../recon_clustering/final/buffers.RData')
load('../recon_clustering/final/clusters.RData')
load('../recon_clustering/registrations.RData')

# Load in recon data
# https://s3.console.aws.amazon.com/s3/object/databrew.org?region=us-east-1&prefix=kwale/recon/clean-form/reconbhousehold/reconbhousehold.csv
recon <- read_csv('from_aws/reconbhousehold.csv')
# https://s3.console.aws.amazon.com/s3/object/databrew.org?region=us-east-1&prefix=kwale/recon/clean-form/reconbhousehold/curated_recon_household_data.csv
recon_curated <- read_csv('from_aws/curated_recon_household_data.csv')

# Read in and organize recon data
hhsp <- readOGR('../../data_public/spatial/households/', 'households')
hhsp@data <- left_join(hhsp@data %>% dplyr::rename(hh_id_clean = hh_id) %>% dplyr::select(-village, ward),
                       recon_curated %>% dplyr::select(hh_id_raw, hh_id_clean,
                                                       community_health_unit,
                                                       village,
                                                       ward))
# See if in cluster core / buffer
o <- sp::over(hhsp, polygons(clusters))
hhsp@data$cluster <- clusters@data$cluster_number[o]
o <- sp::over(hhsp, polygons(buffers))
hhsp@data$buffer <- buffers@data$cluster_number[o]
o <- sp::over(hhsp, polygons(cores))
hhsp@data$core <- cores@data$cluster_number[o]
# Keep only those which are in clusters
hhsp <- hhsp[!is.na(hhsp@data$cluster),]
# Define buffer / core status
hhsp@data$core_buffer <- ifelse(!is.na(hhsp@data$core), 'Core',
                                ifelse(!is.na(hhsp@data$buffer), 'Buffer', NA))
hhsp@data$core_buffer <- factor(hhsp@data$core_buffer, levels = c('Core', 'Buffer'))
hhsp <- hhsp[!is.na(hhsp@data$core_buffer),]


# For each community health unit, get the clusters
x <- hhsp@data %>%
  group_by(community_health_unit, cluster) %>%
  summarise(hh = n()) %>%
  ungroup

# Do by chu
by_chu <- x %>%
  arrange(desc(hh)) %>%
  group_by(community_health_unit) %>%
  summarise(n_clusters = n(),
            n_households = sum(hh),
            clusters = paste0('Cluster ', cluster, ' (', hh, ' households)', collapse = '; '))
names(by_chu) <- toupper(names(by_chu))
names(by_chu) <- gsub('_', ' ', names(by_chu))
dt <- bohemia::prettify(by_chu, nrows = nrow(by_chu),
                  download_options = TRUE)

# htmltools::save_html(dt, file = '~/Desktop/by_chu.html')
# htmlwidgets::saveWidget(dt, file = 'chu.html')
```

# Which clusters are in each CHU (community health unit)?

```{r}
dt
```

# Which CHUs are in each cluster?

```{r}
# Do by chu
by_cluster <- x %>%
  arrange(desc(hh)) %>%
  group_by(cluster) %>%
  summarise(n_chus = n(),
            n_households = sum(hh),
            chus = paste0('CHU ', community_health_unit, ' (', hh, ' households)', collapse = '; '))
names(by_cluster) <- toupper(names(by_cluster))
names(by_cluster) <- gsub('_', ' ', names(by_cluster))

```

# Which clusters are in each CHU (community health unit)?

```{r}
bohemia::prettify(by_cluster, nrows = nrow(by_cluster),
                  download_options = TRUE)
```

# In which cluster does each CHV work (per recon geocoding)?

```{r}
p275 <- read_csv('275.csv') # https://bohemia.team/kenyaclusterdetails/
pd <- recon %>%
  mutate(wid = ifelse(is.na(wid_qr), wid_manual, wid_qr)) %>%
  dplyr::select(longitude = Longitude, 
                latitude = Latitude, wid) %>%
  mutate(x = longitude, y = latitude) %>%
  filter(!is.na(longitude))
coordinates(pd) <- ~x+y
proj4string(pd) <-  "+proj=longlat +ellps=WGS84 +datum=WGS84 +no_defs"
o <- sp::over(pd, polygons(clusters))
pd$cluster_number <- clusters$cluster_number[o]
pdx <- pd@data %>%
  filter(!is.na(cluster_number))  %>%
  group_by(wid) %>%
  summarise(n_clusters = length(unique(cluster_number)),
            n_households = n(),
            clusters = paste0(sort(unique(cluster_number)), collapse = '; ')) 
# Calculate number of fieldworkers, adding up ALL the clusters associated with
# that fieldworker
pdx$n_fieldworkers <- pdx$fieldworkers_details <- NA
for(i in 1:nrow(pdx)){
  this_row <- pdx[i,]
  these_clusters <- this_row$clusters
  these_clusters <- sort(unique(as.numeric(unlist(strsplit(these_clusters, '; ')))))
  sub_275 <- p275 %>% filter(`Cluster number` %in% these_clusters) %>%
    arrange(`Cluster number`)
  pdx$n_fieldworkers[i] <- sum(sub_275$Fieldworkers)
  pdx$fieldworkers_details[i] <- sub_275 %>% mutate(x = paste0('Cluster ', `Cluster number`, ': ', Fieldworkers, ' fieldworkers. ')) %>% pull(x) %>% paste0(collapse = '')
}
names(pdx) <- toupper(names(pdx))
names(pdx) <- gsub('_', ' ', names(pdx))
dt <- bohemia::prettify(pdx, nrows = nrow(pdx),
                  download_options = TRUE)

dt
```


# Which WID (worker IDs) are associated with each cluster?

```{r}
pd <- recon %>%
  mutate(wid = ifelse(is.na(wid_qr), wid_manual, wid_qr)) %>%
  dplyr::select(longitude = Longitude, 
                latitude = Latitude, wid) %>%
  mutate(x = longitude, y = latitude) %>%
  filter(!is.na(longitude))
coordinates(pd) <- ~x+y
proj4string(pd) <-  "+proj=longlat +ellps=WGS84 +datum=WGS84 +no_defs"
o <- sp::over(pd, polygons(clusters))
pd$cluster_number <- clusters$cluster_number[o]
pdx <- pd@data %>%
  filter(!is.na(cluster_number))  %>%
  group_by(cluster_number) %>%
  summarise(n_wids = length(unique(wid)),
            wids = paste0(sort(unique(wid)), collapse = '; ')) 
names(pdx) <- toupper(names(pdx))
names(pdx) <- gsub('_', ' ', names(pdx))
dt <- bohemia::prettify(pdx, nrows = nrow(pdx),
                  download_options = TRUE)

```

# Which "areas of work" are associated with each cluster?  (using `registration` data)

```{r}
right <- registrations %>%
  filter(worker_type == 'CHV') %>%
  mutate(wid = ifelse(is.na(wid_qr), wid_manual, wid_qr)) %>%
  mutate(areas_of_work = paste0(villages_chv, villages_chv_specify)) %>%
  dplyr::select(areas_of_work, wid)
pd <- recon %>%
  mutate(wid = ifelse(is.na(wid_qr), wid_manual, wid_qr)) %>%
  dplyr::select(longitude = Longitude, 
                latitude = Latitude, wid) %>%
  mutate(x = longitude, y = latitude) %>%
  filter(!is.na(longitude)) %>%
  left_join(right)
coordinates(pd) <- ~x+y
proj4string(pd) <-  "+proj=longlat +ellps=WGS84 +datum=WGS84 +no_defs"
o <- sp::over(pd, polygons(clusters))
pd$cluster_number <- clusters$cluster_number[o]
pdx <- pd@data %>%
  filter(!is.na(cluster_number))  %>%
  group_by(cluster_number) %>%
  summarise(n_villages = length(unique(areas_of_work)),
            villages = paste0(sort(unique(areas_of_work)), collapse = '; ')) 
names(pdx) <- toupper(names(pdx))
names(pdx) <- gsub('_', ' ', names(pdx))
dt <- bohemia::prettify(pdx, nrows = nrow(pdx),
                  download_options = TRUE)

dt
```


# Which clusters are associated with each "area of work"? (using `registration` data)

Note that the "areas of work" question had possibly >1 response, and it's not clear from recon registrations which houses are associated with each

```{r}
right <- registrations %>%
  filter(worker_type == 'CHV') %>%
  mutate(wid = ifelse(is.na(wid_qr), wid_manual, wid_qr)) %>%
  mutate(areas_of_work = paste0(villages_chv, villages_chv_specify)) %>%
  dplyr::select(areas_of_work, wid)
pd <- recon %>%
  mutate(wid = ifelse(is.na(wid_qr), wid_manual, wid_qr)) %>%
  dplyr::select(longitude = Longitude, 
                latitude = Latitude, wid) %>%
  mutate(x = longitude, y = latitude) %>%
  filter(!is.na(longitude)) %>%
  left_join(right)
coordinates(pd) <- ~x+y
proj4string(pd) <-  "+proj=longlat +ellps=WGS84 +datum=WGS84 +no_defs"
o <- sp::over(pd, polygons(clusters))
pd$cluster_number <- clusters$cluster_number[o]
pdx <- pd@data %>%
  filter(!is.na(cluster_number))  %>%
  group_by(areas_of_work) %>%
  summarise(n_clusters = length(unique(cluster_number)),
            clusters = paste0(sort(unique(cluster_number)), collapse = '; ')) 
names(pdx) <- toupper(names(pdx))
names(pdx) <- gsub('_', ' ', names(pdx))
dt <- bohemia::prettify(pdx, nrows = nrow(pdx),
                  download_options = TRUE)
dt
```


# Which "areas of work" are associated with each cluster?  (using `recon` data)

```{r}
pd <- recon %>%
  mutate(wid = ifelse(is.na(wid_qr), wid_manual, wid_qr)) %>%
  dplyr::select(longitude = Longitude, 
                latitude = Latitude, wid,
                areas_of_work = village) %>%
  mutate(x = longitude, y = latitude) %>%
  filter(!is.na(longitude)) 
coordinates(pd) <- ~x+y
proj4string(pd) <-  "+proj=longlat +ellps=WGS84 +datum=WGS84 +no_defs"
o <- sp::over(pd, polygons(clusters))
pd$cluster_number <- clusters$cluster_number[o]
pdx <- pd@data %>%
  filter(!is.na(cluster_number))  %>%
  group_by(cluster_number) %>%
  summarise(n_villages = length(unique(areas_of_work)),
            villages = paste0(sort(unique(areas_of_work)), collapse = '; ')) 
names(pdx) <- toupper(names(pdx))
names(pdx) <- gsub('_', ' ', names(pdx))
dt <- bohemia::prettify(pdx, nrows = nrow(pdx),
                  download_options = TRUE)
dt
```

# Which clusters are associated with each "area of work"? (using `recon`` data)


```{r}
pd <- recon %>%
  mutate(wid = ifelse(is.na(wid_qr), wid_manual, wid_qr)) %>%
  dplyr::select(longitude = Longitude, 
                latitude = Latitude, wid,
                areas_of_work = village) %>%
  mutate(x = longitude, y = latitude) %>%
  filter(!is.na(longitude))
coordinates(pd) <- ~x+y
proj4string(pd) <-  "+proj=longlat +ellps=WGS84 +datum=WGS84 +no_defs"
o <- sp::over(pd, polygons(clusters))
pd$cluster_number <- clusters$cluster_number[o]
pdx <- pd@data %>%
  filter(!is.na(cluster_number))  %>%
  group_by(village = areas_of_work) %>%
  summarise(n_clusters = length(unique(cluster_number)),
            clusters = paste0(sort(unique(cluster_number)), collapse = '; ')) 
names(pdx) <- toupper(names(pdx))
names(pdx) <- gsub('_', ' ', names(pdx))
dt <- bohemia::prettify(pdx, nrows = nrow(pdx),
                  download_options = TRUE)
dt
```


# Map

```{r}
pd <- recon %>%
  mutate(wid = ifelse(is.na(wid_qr), wid_manual, wid_qr)) %>%
  dplyr::select(longitude = Longitude, 
                latitude = Latitude, wid,
                village) %>%
  mutate(x = longitude, y = latitude) %>%
  filter(!is.na(longitude)) 
coordinates(pd) <- ~x+y
proj4string(pd) <-  "+proj=longlat +ellps=WGS84 +datum=WGS84 +no_defs"
o <- sp::over(pd, polygons(clusters))
pd <- pd[!is.na(o),]
wids <- sort(unique(pd$wid))
cols <- rainbow(length(wids))
library(leaflet)
l <- leaflet() %>%
  addTiles() %>%
  addPolygons(data = clusters, label = clusters$cluster_number,
              popup = clusters$cluster_number,
              fillColor = 'black',
              color = 'black') 
for(i in 1:length(wids)){
  this_wid <- wids[i]
  this_color <- cols[i]
  z <-  pd[pd@data$wid == this_wid,]
  l <- l %>%
    addCircleMarkers(data = z,
                    
                     radius = 3,
                     fillOpacity = 1,
                     fillColor = this_color,
                     weight = 0,
                     color = this_color,
                     label = paste0(z$wid, '. ', z$village),
                     popup = paste0(z$wid, '. ', z$village))
}
l
  # addMarkers(data = pd, popup = pd$village, label = pd$village, clusterOptions = markerClusterOptions())
```

